Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-06-03 02_paper/02_study/paper_methods.Rmd
update method

  We received funding from QualiFond of University Leipzig. We have no conflicts of interest to disclose. This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11 2022; EARLI SIG 27, 2022).

@@

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable)

@@

# creating new column with percent of gender
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(Gender_Sum=n())

@@

@@

## Material

Experimental stimuli are freely available in the following online repository: https://github.com/... .

@@

During the lesson, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/). The system consisted of a wearable head unit and a recording unit. As shown in Figure \@ref(fig:tobiiglasses2), the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher’s field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \@ref(fig:teachersgaze). The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).

@@

### Behavioral data

The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder (https://zoomcorp.com/en/gb/handheld-recorders/handheld-recorders/h3-vr-360-audio-recorder/) installed in the middle of the lab setting. The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.

Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf) from different angles.  The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.

@@

### Verbal data

In addition to the eye-tracking, questionnaire and behavioral data, verbal data was also collected in the form of a Stimulated Recall Interview.

@@

@@

Finally, the test persons answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management.

>>>>

  We received funding from QualiFond of University Leipzig. We have no conflicts of interest to disclose. This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).

@@

needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools)

@@

# creating new column with total participants to calculate percent of gender
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(Gender_Sum=n())

# changing Type of School into character
# LI18:
# 1: Grundschule
# 2: Oberschule
# 3: Gymnasium
# 4: Förderschule/Sondershausen
# 5: Berufsbildende Schule
# -1: andere Schulform
demo.data$`Type of School` <- factor(x = demo.data$`Type of School`,
                   levels = c("1","2","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$`Type of School`)
                   labels = c("Grundschule","Oberschule","Gymnasium","Förderschule","Berufsbildende Schule", "andere Schulform")) # Bezeichnungen

@@

### XXX Type of School noch eintragen

@@

## Variables

All stimuli are freely available in the following online repository: https://github.com/... .

@@

To record eye-tracking data, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker during the micro-teaching-unit. The system consisted of a wearable head unit and a recording unit. As shown in Figure \@ref(fig:tobiiglasses2), the head unit was a measuring device with different sensors. A high-definition scene camera captured a full HD video of the teacher’s field of vision. An integrated microphone recorded the surrounding sounds. Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \@ref(fig:teachersgaze). The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second. The scene camera had a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).

@@

### Video data

The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \@ref(fig:setup). The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.

Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \@ref(fig:setup). The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.

@@

#### Rating scales

@@

#### Situational Jugdement Test
To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]).

Gold and Holodynski (2015, p. 229) developed a 'Situational Judgment Test of Strategic Knowledge of Classroom Management in Elementary Schools (SJT)' to measure strategic knowledge of classroom management among elementary school teachers. This is a test procedure for situation-specific action in which the participants are presented with hypothetical scenarios for which they are to indicate how a teacher should ideally behave or how promising the presented options for action are on the basis of given answer options.

In developing the test procedure, the authors divided the concept of classroom management into three main aspects: *Monitoring*, *managing momentum* (structuring) and *rules and routines* [@gold2015development, p. 230f].

*Monitoring* includes proactive strategies such as omnipresence. This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them. The second strategy is overlapping. In this case, the teacher is able to control several teaching processes at the same time. Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf. ibid.; [@kounin2006techniken, p. 89ff).

By *managing momentum* (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p. 101ff]. They also include the group focus specifically identified by Kounin [@kounin2006techniken, p. 117ff], i.e. mobilizing the whole class and demanding accountability [@gold2015development, p. 231].

The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers the pupils, orientation and structure in everyday school life (cf. ibid.).

When taking the test, participants must rate all six response options for each scenario as suitable or unsuitable using a six-point scale (see sample scenario in Appendix 1). Prior to this, the effectiveness of the strategies proposed in the answers was determined by expert judgement. Based on these, an overall rating was created, which is used for the evaluation of the answer keys. All three mentioned knowledge facets of class management (monitoring, transition design and rules and routines) are recorded separately with separate tasks in this SJT by Gold and Holodynski. The original 14 individual scenarios can each be assigned to one facet: Scenarios 1-5 cover the area of ubiquity, scenarios 6-10 the area of structuring and scenarios 11-14 the area of rules and routines. Scenarios 10 and 12 were removed from the test due to insufficient agreement between the expert judgement. In the evaluation, in addition to an overall assessment, all three knowledge areas can be presented and compared individually.

@@

Finally, the subjects answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management.

### 2022-06-03 02_paper/02_study/paper_methods.tex
update method

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking\newline\indent Word count: XXX}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

@@

\begin{tabular}{llllllllllllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
\midrule
Expert & 7 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
Novice & 21 & 0.00 & 0.00 & 0.00 & 0.00 & 7.40 & 2.50 & 3.00 & 11.00 & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
\bottomrule
\end{tabular}

@@

The novice teachers (13 women; 61.90\%) had a mean age of 23.30 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their 7.40 semester (\emph{SD} = 2.50; range: 3-11). Furthermore, they had an average teaching experience of 12 teaching units à 45min (\emph{SD} = 8.60; range: 0-36) through the internships during their studies. 90.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking\newline\indent Word count: XXX}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\begin{verbatim}
## Warning: NAs durch Umwandlung erzeugt
\end{verbatim}

@@

\begin{tabular}{llllllllllllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
\midrule
Expert & 7 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
Novice & 21 & 0.00 & 0.00 & 0.00 & 0.00 & NA & NA & NA & NA & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
\bottomrule
\end{tabular}

@@

The novice teachers (13 women; 61.90\%) had a mean age of 23.30 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years. On average, the student teachers were in their NA semester (\emph{SD} = NA; range: NA-NA). Furthermore, they had an average teaching experience of 12 teaching units à 45min (\emph{SD} = 8.60; range: 0-36) through the internships during their studies. 90.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
